Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-13 Paper/paper.tex
Update text

>>>>

\section{Comparison with other luminosity function determinations}

Figure~\ref{fig:params_grand} compares the parameters of the double
power law luminosity function from our analysis of
Section~\ref{sec:bins} to values reported in the literature.  In
general, our break luminosity is brighter and the faint-end slope is
steeper than other determinations.  Note however that several results
from the literature shown in Figure~\ref{fig:params_grand} make
restrictive assumptions while fitting double power law models to data.
For example, \citet{2013ApJ...768..105M} fix the bright-end slope
$\alpha$ to $-4$ at $z=4.7$--$5.1$.  \citet{2016ApJ...833..222J} fix
the faint-end slope $\beta$ to $-2.8$ at $z=5.7$--$6.4$.
\citet{2017ApJ...847L..15O} fix the bright-end slope $\alpha$ to
$-2.8$ at $z=5.5$--$6.5$.  \citet{2015AA...578A..83G} fix the
faint-end slope and the break luminosity in their highest-redshift bin
($z=5.0$--$6.5$).  The choice of data sets is also often different.
For instance, \citet{2015AA...578A..83G} do not include the SDSS
Stripe 82 data from \citet{2013ApJ...768..105M} and the AGN samples of
\citet{2010AJ....139..906W} and \citet{2015ApJ...798...28K} in their
analysis.  (We discuss the results of \citet{2015AA...578A..83G} in
greater detail in Appendix~\ref{sec:conv}.)  Of the remaining
determinations, our parameter values are closest to those reported by
\citet{2016ApJ...829...33Y} at $z=4.7$--$5.4$.

\begin{figure*}
  \begin{center}
    % summary_grand.py
    \includegraphics[width=0.7\textwidth]{evolution_grand.pdf}
  \end{center}
  \caption{A comparison of our inferred double power law parameter
    values with those reported in the literature.  Black points show
    our determinations from Figure~\ref{fig:evoln}.  Blue points show
    other values, from \citet[triangles]{2012ApJ...755..169M},
    \citet[squares]{2016ApJ...833..222J},
    \citet[diamonds]{2011ApJ...728L..26G},
    \citet[crosses]{2013ApJ...768..105M}, \citet[downward
      triangles]{2015AA...578A..83G},
    \citet[pentagons]{2018PASJ...70S..34A}, \citet[leftward
      triangles]{2017ApJ...847L..15O},
    \citet[asterisks]{2016ApJ...829...33Y},
    \citet[circles]{2013ApJ...773...14R}, and \citet[rightward
      triangles]{2009A&A...507..781S}.  Where necessary, values from
    the literature have been converted to our cosmology.
    \label{fig:params_grand}}
\end{figure*}
